%------------------------------------------------------------------------------
% Semiconductor-focused CV for AMD Shanghai
%------------------------------------------------------------------------------

\documentclass[a4paper,11pt]{article}

\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{xcolor}
\usepackage{tabularx}

%-----PAGE SETUP---------------------------------------------------------------

\addtolength{\oddsidemargin}{-1cm}
\addtolength{\evensidemargin}{-1cm}
\addtolength{\textwidth}{2cm}
\addtolength{\topmargin}{-1cm}
\addtolength{\textheight}{2cm}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0cm}

%-----SECTION FORMATTING-------------------------------------------------------

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-----CUSTOM COMMANDS----------------------------------------------------------

\newcommand{\CVItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\CVSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \small#3 & \small #4 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\CVProjectHeading}[2]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\CVSubHeadingListStart}{\begin{itemize}[leftmargin=0.5cm, label={}]}
\newcommand{\CVSubHeadingListEnd}{\end{itemize}}
\newcommand{\CVItemListStart}{\begin{itemize}[leftmargin=0.55cm]}
\newcommand{\CVItemListEnd}{\end{itemize}\vspace{-5pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

%------------------------------------------------------------------------------
% CV STARTS HERE
%------------------------------------------------------------------------------

\begin{document}

%-----HEADING------------------------------------------------------------------

\begin{center}
  \textbf{\LARGE \scshape Tianyi ZHANG} \\ \vspace{2pt}
  \small Pudong New District, Shanghai, China $|$
  +86 13307187701 $|$
  \href{mailto:zhangtianyi2023aa@163.com}{zhangtianyi2023aa@163.com}
\end{center}

%-----OBJECTIVE----------------------------------------------------------------

\section{Objective}
\small{
Seeking semiconductor engineering opportunities at \textbf{AMD Shanghai}, with a focus on SoC verification, automation infrastructure, AI-assisted EDA tooling, and hardware/software workflow optimisation.
}

%-----EDUCATION----------------------------------------------------------------

\section{Education}
\CVSubHeadingListStart

\CVSubheading
{MSc Precision Scientific Instrumentation}
{Expected 2026 -- 2027}
{Nanyang Technological University}
{Singapore}
\CVItemListStart
  \CVItem{Focus on semiconductor instrumentation, precision electronics, sensing systems, and advanced hardware integration.}
\CVItemListEnd

\CVSubheading
{BEng Mechanical Engineering \emph{\small{(First Class Honours)}}}
{Sept 2023 -- Jun 2026}
{University College London}
{London, United Kingdom}
\CVItemListStart
  \CVItem{First Class Honours, approximately equivalent to GPA 3.7+/4.0 in the Chinese grading system.}
  \CVItem{Relevant coursework: control systems, simulation and modelling, numerical methods, data structures, embedded systems.}
\CVItemListEnd

\CVSubHeadingListEnd

%-----SKILLS-------------------------------------------------------------------

\section{Skills}
\begin{itemize}[leftmargin=0.5cm, label={}]
    \item \small{\textbf{Programming:} Python, Java, C++, MATLAB, Shell, Verilog}
    \item \small{\textbf{Semiconductor \& Verification Tools:} Synopsys VCS, Verdi, Linux, Perforce, RTL automation, regression testing}
    \item \small{\textbf{Software \& Data Systems:} FastAPI, Streamlit, SQL, Git, data processing pipelines, statistical forecasting}
    \item \small{\textbf{Engineering Tools:} MATLAB Simulink, LabVIEW, ANSYS, Fusion 360}
\end{itemize}

%-----WORK EXPERIENCE----------------------------------------------------------

\section{Work Experience}
\CVSubHeadingListStart

\CVSubheading
{Assistant Project Engineer, MSIP Department}
{Jul 2024 -- Present}
{Advanced Micro Devices, Inc. (AMD)}
{Shanghai / London}
\CVItemListStart
  \CVItem{Contributed to memory read/write IP development for AMD accelerator projects including MI350 and MI400.}
  \CVItem{Developed automation and AI-assisted verification scripts for large-scale SoC signal inspection and traffic analysis.}
  \CVItem{Built automated RTL error-injection frameworks to improve verification robustness and functional coverage evaluation.}
  \CVItem{Maintained regression and validation workflows using Linux, Shell scripting, Python, Perforce, Synopsys VCS, and Verdi.}
  \CVItem{Improved internal AI scripting tools by integrating intelligent command correction features to reduce user input errors.}
\CVItemListEnd

\CVSubHeadingListEnd

%-----PROJECTS-----------------------------------------------------------------

\section{Projects}
\CVSubHeadingListStart

\CVProjectHeading
{Full-Stack Immigration Data Management System $|$ \emph{\small{FastAPI / Streamlit / SQL}}}
{2025}
\CVItemListStart
  \CVItem{Developed a full-stack data management platform for the Singapore Immigration \& Checkpoints Authority (ICA).}
  \CVItem{Designed backend APIs and database structures using FastAPI for traveller record management and analytics.}
  \CVItem{Built Streamlit dashboards for operational monitoring, data interaction, and visual analysis.}
  \CVItem{Implemented short-term forecasting models to estimate future inbound traveller volume trends.}
  \CVItem{Integrated automated data-processing pipelines to support decision-making workflows.}
\CVItemListEnd

\CVProjectHeading
{Energy-Aware Route Optimisation for Electric Scooters $|$ \emph{\small{OSM / Graph Algorithms}}}
{2025 -- Jun 2026}
\CVItemListStart
  \CVItem{Developed a simulation framework for electric scooter energy modelling using real-world map and elevation data.}
  \CVItem{Implemented graph-based routing algorithms with custom energy-consumption edge weights derived from terrain and traffic conditions.}
  \CVItem{Designed a hybrid optimisation strategy combining regenerative braking analysis with energy-aware route planning.}
  \CVItem{Built automated simulation pipelines for large-scale route evaluation and statistical comparison across urban scenarios.}
\CVItemListEnd

\CVProjectHeading
{Path Planning for Trailer Obstacle Avoidance $|$ \emph{\small{A* Algorithms / Kinematic Constraints}}}
{2022 -- 2023}
\CVItemListStart
  \CVItem{Developed a constrained path-planning framework for articulated trailer systems using an enhanced A* search algorithm.}
  \CVItem{Integrated non-holonomic vehicle dynamics, steering continuity constraints, and collision-envelope detection into the planning heuristic.}
  \CVItem{Generated dynamically feasible obstacle-avoidance trajectories while balancing computational efficiency and path optimality.}
\CVItemListEnd

\CVSubHeadingListEnd

%-----LEADERSHIP---------------------------------------------------------------

\section{Leadership \& Activities}
\CVSubHeadingListStart

\CVProjectHeading
{UCL Racing Formula E Team}
{Nov 2023 -- Jun 2026}
\CVItemListStart
  \CVItem{Assisted in debugging motor signals and sensor feedback systems for the Formula E race car.}
\CVItemListEnd

\CVProjectHeading
{Vice President \& Director of Program Control, Robotics Club}
{Sept 2020 -- Jun 2023}
\CVItemListStart
  \CVItem{Led the construction and debugging of robotic control modules and competed in the FRC China Regional Competition.}
\CVItemListEnd

\CVSubHeadingListEnd

%-----AWARDS-------------------------------------------------------------------

\section{Honors \& Awards}
\CVSubHeadingListStart

\CVProjectHeading
{British Physics Olympiad Gold Award}
{Nov 2022}

\CVSubHeadingListEnd

%-----ADDITIONAL INFORMATION---------------------------------------------------

\section{Additional Information}
\begin{itemize}[leftmargin=0.5cm, label={}]
    \item \small{\textbf{Languages:} Chinese Native, English Professional Working Proficiency}
    \item \small{\textbf{Interests:} Football, Table Tennis, Reading, Travelling}
\end{itemize}

\end{document}